### 2017-08-28 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic XRD - Proof read and made minor edits

%Table of Contents
%\clearpage
\newpage
\tableofcontents\newpage
\addcontentsline{toc}{section}{TABLE OF CONTENTS}
\clearpage %% start of main matter

@@

In the bulk a double peak at 38\degree~ and 39\degree~ begins to emerge at 125\degree C, phases which never evolve in the film. The bulk \CaMgZnFive~ peaks at 42.3\degree~ and 43.7\degree~ start to emerge at 165\degree C and 170\degree C respectively, but are never seen in the film. A faint \MgZn~ and \CaMgZnFive~ peak at 53.3\degree is seen in the bulk at 175\degree C, but never in the film. The final small Mg and \MgZn~ 57.2\degree~ peak at 170\degree C is also never seen in the film. These observations are tabulated in Table \ref{tab:Dynamic_XRD}. The bulk \acrshort{xrd} is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and the film in Figure \ref{fig:XRD_Dynamic_Film}. Normalised plots allowing for easy identification of differences between the bulk and film are shown in Figures \ref{fig:XRD_Dynamic_185}, \ref{fig:XRD_Dynamic_145}, and \ref{fig:XRD_Dynamic_105}.

\begin{table}[h]
	\centering
	\caption{Main dynamic \gls{xrd} peaks for both the bulk and the film. Data shows minor shifting for peaks 3 and 8, large start temperature differences for peaks 1 and 2, and failure of peaks $4-7$, 9, and 10 to nucleation in the film.}
	\begin{tabular}{ c c c c c c c c }
		\toprule
		Peak & Bulk & Film & Change & Bulk Start & Film Start & Change & Phases \\
		& $2\theta$ & $2\theta$ & \% & \degree C & \degree C & \% & at\% \\
		\midrule
		1    & 32.1 & 32.1 & 0.0\%  & 170 & 90 & -47.1\% & Mg, \MgZn \\
		2    & 34.3 & 34.3 & 0.0\%  & 75  & 115 & 53.3\% & Mg, \MgZn, \CaMgZnFive \\
		3    & 36.6 & 36.5 & -0.3\% & 130 & 130 & 0.0\%  & Mg, \MgZn \\
		4    & 38.0 & N/A  & N/A    & 125 & N/A & N/A    & \MgZn, \CaMgZnFive \\
		5    & 39.0 & N/A  & N/A    & 125 & N/A & N/A    & \MgZn \\
		6    & 42.3 & N/A  & N/A    & 165 & N/A & N/A    & \CaMgZnFive \\
		7    & 43.7 & N/A  & N/A    & 170 & N/A & N/A    & \CaMgZnFive \\
		8    & 47.7 & 47.6 & -0.2\% & 170 & 170 & 0.0\%  & Mg, \MgZn \\
		9    & 53.3 & N/A  & N/A    & 175 & N/A & N/A    & \MgZn, \CaMgZnFive \\
		10   & 57.2 & N/A  & N/A    & 170 & N/A  & N/A   & Mg, \MgZn \\
		\bottomrule
	\end{tabular}
	\label{tab:Dynamic_XRD}
\end{table}

It was also observed that there was a some minor peak shifting between the Mg, \MgZn, and \CaMgZnFive~ phases in the dynamic bulk and film \acrshort{xrd}. The largest shifts were seen in the \CaMgZnFive~ 34.6\degree~ peak and \MgZn~ 39.1\degree~ peak of 1.4\% and 1.0\% respectively. These shifts are tabulated in Table \ref{tab:Dynamic_XRD_PeakShift}.

\begin{table}[h]
	\centering
	\caption{Location of the bulk and film peaks for the dynamic \acrshort{xrd} Mg, \MgZn, and \CaMgZnFive~ compounds.}
	\begin{tabular}{ c c c c c c c c c }
		\toprule
		\multicolumn{3}{c}{Mg} & \multicolumn{3}{c}{\MgZn} & \multicolumn{3}{c}{\CaMgZnFive} \\
		Bulk & Film & Change \% & Bulk & Film & Change \% & Bulk & Film & Change \% \\
		\midrule
		32.1 & 32.1 & 0.0\%  & 32.1 & 32.1   & 0.0\%  & 34.1 & 34.1 & 0.0\% \\
		34.3 & 34.3 & 0.0\%  & 34.3 & 34.3   & 0.0\%  & 34.6 & 35.1 & 1.4\% \\
		36.6 & 36.5 & -0.3\% & 36.6 & 36.5   & -0.3\% & 36.0 & 35.7 & -0.8\% \\
		47.7 & 47.6 & -0.2\% & 38.0 & 38.2   & 0.5\%  & 38.0 & 38.2 & 0.5\% \\
		57.2 & 57.1 & -0.2\% & 39.1 & 39.5   & 1.0\%  & 42.3 & 42.2 & -0.2\% \\
		&    &      & 45.1   & 45.2 & 0.2\%  & 43.7   & 43.3 & -0.9\% \\
		&    &      & 47.7   & 47.6 & -0.2\% & 53.3   & 53.0 & -0.6\% \\
		&    &      & 53.3   & 53.0 & -0.6\% &        &      &        \\
		&    &      & 57.2   & 57.1 & -0.2\% &        &      &        \\
		\bottomrule
	\end{tabular}
	\label{tab:Dynamic_XRD_PeakShift}
\end{table}

>>>>

%Table of Contents
%\clearpage
\newpage
\addcontentsline{toc}{section}{TABLE OF CONTENTS}
\tableofcontents\newpage
\clearpage %% start of main matter

@@

In the bulk a double peak at 38\degree~ and 39\degree~ begins to emerge at 125\degree C, phases which never evolve in the film. The bulk \CaMgZnFive~ peaks at 42.3\degree~ and 43.7\degree~ start to emerge at 165\degree C and 170\degree C respectively, but are never seen in the film. A faint \MgZn~ and \CaMgZnFive~ peak at 53.3\degree is seen in the bulk at 175\degree C, but never in the film. The final small Mg and \MgZn~ 57.2\degree~ peak at 170\degree C is also never seen in the film. These observations are tabulated in Table \ref{tab:Dynamic_XRD}. The bulk dynamic \acrshort{xrd} is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and the film in Figure \ref{fig:XRD_Dynamic_Film}. Normalised plots allowing for easy identification of differences between the bulk and film are shown in Figures \ref{fig:XRD_Dynamic_185}, \ref{fig:XRD_Dynamic_145}, and \ref{fig:XRD_Dynamic_105}.

\begin{table}[h]
	\centering
	\caption{Main dynamic \acrshort{xrd} peaks for both the bulk and the film. Data shows minor shifting for peaks 3 and 8, large start temperature differences for peaks 1 and 2, and failure of peaks $4-7$, 9, and 10 to nucleation in the film.}
	\begin{tabular}{ c c c c c c c c }
		\toprule
		Peak & Bulk & Film & Change & Bulk Start & Film Start & Change & Phases \\
		& $2\theta$ & $2\theta$ & \% & \degree C & \degree C & \% & at\% \\
		\midrule
		1    & 32.1 & 32.1 & 0.0\%  & 170 & 90 & -47.1\% & Mg, \MgZn \\
		2    & 34.3 & 34.3 & 0.0\%  & 75  & 115 & 53.3\% & Mg, \MgZn, \CaMgZnFive \\
		3    & 36.6 & 36.5 & -0.3\% & 130 & 130 & 0.0\%  & Mg, \MgZn \\
		4    & 38.0 & N/A  & N/A    & 125 & N/A & N/A    & \MgZn, \CaMgZnFive \\
		5    & 39.0 & N/A  & N/A    & 125 & N/A & N/A    & \MgZn \\
		6    & 42.3 & N/A  & N/A    & 165 & N/A & N/A    & \CaMgZnFive \\
		7    & 43.7 & N/A  & N/A    & 170 & N/A & N/A    & \CaMgZnFive \\
		8    & 47.7 & 47.6 & -0.2\% & 170 & 170 & 0.0\%  & Mg, \MgZn \\
		9    & 53.3 & N/A  & N/A    & 175 & N/A & N/A    & \MgZn, \CaMgZnFive \\
		10   & 57.2 & N/A  & N/A    & 170 & N/A  & N/A   & Mg, \MgZn \\
		\bottomrule
	\end{tabular}
	\label{tab:Dynamic_XRD}
\end{table}

It was also observed that there was a some minor peak shifting between the Mg, \MgZn, and \CaMgZnFive~ phases in the dynamic bulk and film \acrshort{xrd}. The largest shifts were seen in the \CaMgZnFive~ 34.6\degree~ peak and \MgZn~ 39.1\degree~ peak, with shifts of 1.4\% and 1.0\% respectively. These shifts are tabulated in Table \ref{tab:Dynamic_XRD_PeakShift}.

\begin{table}[h]
	\centering
	\caption{Location of the dynamic bulk and film \acrshort{xrd} peaks for the Mg, \MgZn, and \CaMgZnFive~ compounds.}
	\begin{tabular}{ c c c c c c c c c }
		\toprule
		\multicolumn{3}{c}{Mg} & \multicolumn{3}{c}{\MgZn} & \multicolumn{3}{c}{\CaMgZnFive} \\
		Bulk & Film & Change \% & Bulk & Film & Change \% & Bulk & Film & Change \% \\
		\midrule
		32.1 & 32.1 & 0.0\%  & 32.1 & 32.1   & 0.0\%  & 34.1 & 34.1 & 0.0\% \\
		34.3 & 34.3 & 0.0\%  & 34.3 & 34.3   & 0.0\%  & 34.6 & 35.1 & 1.4\% \\
		36.6 & 36.5 & -0.3\% & 36.6 & 36.5   & -0.3\% & 36.0 & 35.7 & -0.8\% \\
		47.7 & 47.6 & -0.2\% & 38.0 & 38.2   & 0.5\%  & 38.0 & 38.2 & 0.5\% \\
		57.2 & 57.1 & -0.2\% & 39.1 & 39.5   & 1.0\%  & 42.3 & 42.2 & -0.2\% \\
		&    &      & 45.1   & 45.2 & 0.2\%  & 43.7   & 43.3 & -0.9\% \\
		&    &      & 47.7   & 47.6 & -0.2\% & 53.3   & 53.0 & -0.6\% \\
		&    &      & 53.3   & 53.0 & -0.6\% &        &      &        \\
		&    &      & 57.2   & 57.1 & -0.2\% &        &      &        \\
		\bottomrule
	\end{tabular}
	\label{tab:Dynamic_XRD_PeakShift}
\end{table}
